---
title: "Relationship between GDP, Life Expectancy, and CO2 emissions"
author: "dtetreault"
date: "2023-01-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## name your chunks!
```{r load-packages}
library(tidyverse)
```

This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r, eval = TRUE, include = TRUE} 

gapminder_1997 <- read_csv("data/gapminder_1997.csv")

```

```{r gdp_lifeexp_1997 plot}

ggplot(data = gapminder_1997) +
  aes(x = gdpPercap, y = lifeExp, color = continent) +
  scale_color_brewer(palette = "Set2") +
  labs(x = "GDP per Capita (USD)", y = "Life Expectancy (Years)", caption = "[[ Data collected courtesy of the UN council on humanitarian research. ]]", title = "Life Expectancy Caps before GDP") +
  geom_point() +
  ggprism::theme_prism()

```


